A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-07 body/rbprm.tex
appendix

However between $W^0$ and $B^{max}$, a trade-off can be found between a necessary and a sufficient condition. We define $W^0_s$ as the volume $W^0$ subject to a scaling transformation by a factor $s \in \mathbb{R}^+$. 
%
We then consider the spaces $C_{reach}^s$
 \begin{equation}
C_{reach}^s = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \wedge W^0_s(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \wedge & A_{trunk}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%
The higher $s$ is, the closer this "reachability condition" is to being sufficient, and if $s=1$, the planner is complete. The parametrization of $s$ allows to find a trade-off between these two desirable properties.
Section~\ref{sec:results} shows that in practice, it is easy to adjust $s$ to keep most of the interesting guides without introducing incorrect guides.

@@

%~ Algorithm~\ref{alg:generate} describe the sampling process for one configuration.

%~ Two user defined numeric values, $LIMIT1$ and $LIMIT2$ are used to ensure that the generation will not loop
%~ infinitely around areas of the workspace where the reachability condition cannot be met.
%~ Two configurations are connected if a linearly interpolated path between them also belongs to 
%~ $C_{reach}$.

%~ \begin{algorithm}
%~ \caption{Generation of a configuration $\mathbf{q}^{0} \in C_{reach}^s$} \label{euclid}
	%~ \begin{algorithmic}[1]
	%~ \Function{GenerateConfiguration}{}
		%~ \State $\mathbf{q}^{0} \gets [0,...,0]^T$ /*Set all DOFs to 0*/
		%~ \State $\textit{ntry1} \gets 0; \textit{ntry2} \gets 0;$
		%~ \While {$\textit{ntry1} < \textit{LIMIT1}$}
			%~ \State Select an obstacle $O_i \in O$
			%~ \While {$\textit{ntry2} < \textit{LIMIT2}$}				
				%~ \State Translate $\mathbf{q}^{0}$ to a random point on the surface of $O_i$
				%~ \State $\mathbf{d} \gets $ Random unit direction
				%~ \While {$W(\mathbf{q}^{0}) \cap O_i \ne \emptyset$}
					%~ \State $\epsilon \gets$ random number, $ 0 < \epsilon \leq 1$
					%~ \State Translate $\mathbf{q}^{0}$ by $\mathbf{u} = \epsilon \mathbf{d}$
					%~ \If {$W^0_s(\mathbf{q}^{0}) \cap O = \emptyset$}
						%~ \State \textbf{return} $\mathbf{q}^{0}$
					%~ \Else
						%~ \State Rotate $\mathbf{q}^{0}$ randomly
						%~ \State $\textit{ntry2} \gets \textit{ntry2} + 1$
					%~ \EndIf
				%~ \EndWhile
			%~ \EndWhile
			%~ \State $\textit{ntry1} \gets \textit{ntry1} + 1$
		%~ \EndWhile
		%~ \State \textbf{return} failure
	%~ \EndFunction
%~ \end{algorithmic}
%~ \label{alg:generate}
%~ \end{algorithm}

%To summarize, in this section we define a class of spaces $C_{reach}^s$.We  propose to use RB-PRM, a sampling based motion planner, to compute guide trajectories entirely contained in $C_{reach}^s$. Such trajectories provide a guaranty that a robot will be able to create contacts along them with a probability depending on a parameter $s$.

>>>>

However between $W^0$ and $B^{max}$, a trade-off can be found between a necessary and a sufficient condition. We define $W^0_s$ as the volume $W^0$ subject to a scaling transformation by a factor $s \in \mathbb{R}^+$. 
%
We then consider the spaces $C_{reach}^s$
 \begin{equation}
C_{reach}^s = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \wedge W^0_s(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \wedge & A_{trunk}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%
The higher $s$ is, the closer this "reachability condition" is to being sufficient, and if $s=1$, the planner is complete. The parametrization of $s$ allows to find a trade-off between these two desirable properties.
As an example, Figure~\ref{fig:hyq_roms} presents the volumes $W$ computed for the HyQ robot.
In Appendix~\ref{app:rom}, we give a generic method to compute these volumes, with the example of HRP-2.
%~ Section~\ref{sec:results} shows that in practice, it is easy to adjust $s$ to keep most of the interesting guides without introducing incorrect guides.

\begin{figure}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/hyq_roms}
  \caption{
           $W$ volumes for HyQ. The green shapes represent the reachable workspace $W^k$ of each limb. The red shape is $W^0$, a scaling of the convex hull
           of the torso of the robot.}
		   \label{fig:hyq_roms}
\end{figure}

@@

### 2015-12-07 body/results.tex
appendix

\subsubsection{HyQ -- Obstacle race:}
In this long scene, HyQ is first required to cross a 55 cm large hole; then, to cross a narrow "bridge", only large of 25 cm,
while maintaining equilibrium

%~ \begin{figure*}
  %~ \centering
  %~ \includegraphics[width=0.5\linewidth]{figures/stair}
  %~ \caption{
           %~ HRP-2 in the steep stair climbing scenario. }
		   %~ \label{fig:stair_robust}
%~ \end{figure*}

@@

\subsubsection{HRP-2 -- Path replanning(Figure~\ref{figures/replanning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications involve replanning.

@@

For each scenario, one can observe that average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. In some cases such as the stair climbing, this computation time is actually negligeable. 
Considering the repartition of the computation time, it appears that the majority of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state of the art IK solutions, we believe there is room
for improving the performances of the algorithm.

@@

\begin{table}[b]
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Generate RB-PRM (offline) & Generating the contact sequence & Number of contact states\\
 \hline
   Truck egress (humanoid) & $ 73 $ & 15 & 10 \\
   Truck egress (insectoid) & $70$ & 23 & 48\\
   Climbing (humanoid)& $25$ &  5 & 15\\
   Climbing (insectoid)  & $ 21 $ & 27 & 51\\
   Crouching (humanoid)& $5$ & 6 & 22 \\
 \end{tabular}
\caption{\textbf{Average time} (in seconds) spent in RB-PRM generation, and the online generation of the contact sequence.}
\label{tab:requestime}
\quad
 \end{table}

 We observe that many contacts are required for the insect, which can be explained by its restricted range of motion.
 The time spent generating the navigation graph is about one minute. The time spent in generating the graph of the climbing scenario,
 despite the relatively open environment, is explained by the additional restrictions imposed on the reachability condition.
 The difficulty to find a balanced configuration essentially influences the time spent generating the contacts.

The number of contacts in the sequence gives a rough estimation of its duration in seconds. Except for the robots crawling out of the truck, all the contact generation are real-time. Additionaly to the quality of the generated trajectories shown in the video, these computation times are a major practical achievement.

%~ \subsection{Early results: manipulating scenario in zero gravity}
%~ In this scenario, we suggest an extension of our framework to manipulation.
%~ We consider the task of rotating a pen using a robotic hand.
%~ A start and goal configurations for the pen are expressed in the world coordinate system.
%~ The problem is automatically reformulated into an equivalent motion planning one for the robotic hand, by expressing its start
%~ and goal configurations in the coordinate system of the pen. In other words, for the planning the pen is considered as a static object, and a feasible motion for the hand
%~ is computed along the pen. Figure {penrot} presents the results obtained with this approach.
%~ Additional work is required to generate feasible manipulation motions.

>>>>

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:hyq_bridge} and~\ref{fig:hyq_obs}):}
In this long scene, HyQ is first required to cross a 55 cm large hole; then, to cross a narrow "bridge", only large of 25 cm,
while maintaining equilibrium.

\begin{figure}
  \centering
  \includegraphics[width=0.4\linewidth]{figures/hyq_bridge}
  \caption{
           HyQ crossing a narrow bridge. }
		   \label{fig:hyq_bridge}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/hyq_obs}
  \caption{
           Crossing a hole contact sequence for HyQ ($b_0 > 4$). }
		   \label{fig:hyq_obs}
\end{figure*}

@@

\subsubsection{HRP-2 -- Path replanning(Figure~\ref{fig:replanning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications involve replanning.

@@

For each scenario, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. In some cases such as the stair climbing, this computation time is actually negligeable. 
Considering the repartition of the computation time, it appears that the majority of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state of the art IK solutions, we believe there is room
for improving the performances of the algorithm.

@@

\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Generate RB-PRM (offline) & Generating the contact sequence & Number of contact states\\
 \hline
   Truck egress (humanoid) & $ 73 $ & 15 & 10 \\
   Truck egress (insectoid) & $70$ & 23 & 48\\
   Climbing (humanoid)& $25$ &  5 & 15\\
   Climbing (insectoid)  & $ 21 $ & 27 & 51\\
   Crouching (humanoid)& $5$ & 6 & 22 \\
 \end{tabular}
\caption{\textbf{Average time} (in seconds) spent in RB-PRM generation, and the online generation of the contact sequence.}
\label{tab:requestime}
\quad
 \end{table*}
